---
title: "p8105_hw5_jl5297"
author: "JunLu"
date: "11/1/2018"
output: github_document
---
```{r setup, include=FALSE}
library(readxl)
library(tidyverse)
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_bw() + theme(legend.position = "bottom"))
```

## Overview
This my fifth-week homework and I am practicing iteration through this homework.

## Problem 1
### 1. Clean data
```{r, message=FALSE}
study_df = 
    tibble(file_name = list.files(path = "./data/study")) %>% 
    mutate(study_data = map(str_c("./data/study/", file_name), ~read_csv(.x))) %>% 
    unnest() %>%
    separate(file_name, into = c("group", "subject_id"), sep = "_") %>% 
    gather(key = "week", value = "value", week_1:week_8) %>% 
    mutate(
        subject_id = str_replace(subject_id, ".csv", ""),
        week = str_replace(week, "week_", ""),
        week = as.integer(week),
        group = factor(group, levels = c("con", "exp"), labels = c("control", "experiment"))
        ) %>% 
    arrange(group, subject_id, week)

str(study_df)
```

* We use `purrr::map` to load the data of each csv file and combine them into one dataset. 
* We keep file names and transform them into two variables (`group` and `subject_id`).
* We use `gather` to go from wide to long formats. 

As a result, this tidy dataset contains `r nrow(study_df)` observations and `r ncol(study_df)` variables.

* `group`: (factor) denote which group this subject is belong to, experiment or control group
* `subject_id`: (chr) id number of the subject
* `week`: (int) week of the observation
* `value`: (num) observation vlaue


### 2. Make a spaghetti plot
```{r, message=FALSE}
study_df %>% 
    mutate(id = str_c(group, subject_id)) %>% 
    ggplot(aes(x = week, y = value, color = group)) + 
    geom_line(aes(group = id)) +
    geom_smooth(se = F, size = 2) +
    labs(
        title = "Spaghetti Plot of Observations on Each Subject over Time",
        x = "Week",
        y = "Observation Value"
    )
```

Make a spaghetti plot showing observations on each subject over time. 
From the plot, we can know that 

* Participants in experiment group tended to have a growth trend of observation value over weeks.
* Participants in control group tended to have a relatively steady observation value over weeks.
* Participants in experiment group tended to have higher observation value than participants in control group over weeks.

## Problem 2
### 1. Read the data
```{r}
homicide = read_csv("./data/homicide-data.csv", col_types = "cccccccccddc")
str(homicide)
```
We load the raw data from "homicide-data.csv" and it contains `r nrow(homicide)` observations and `r ncol(homicide)` variables. The data included the location of the killing, whether an arrest was made and, in most cases, basic demographic information about each victim.

* `uid`: (chr) unique identifier for each homicide record
* `reported_date`: (chr) reported date 
* `victim_last`: (chr) victim last name
* `victim_first`: (chr) victim first name
* `victim_race`: (chr) victim race
* `victim_age`: (chr) victim age
* `victim_sex`: (chr) victim age
* `city`: (chr) occurrence city
* `state`: (chr) occurrence state
* `lat`: (num) occurrence latitude
* `lon`: (num) occurrence longitude
* `disposition`: dispostion result(whether an arrest was made)

### 2. Clean the data
```{r}
homicide_tidy = 
    homicide %>% 
    mutate(city_state = str_c(city, ", ", state)) %>% 
    group_by(city_state) %>% 
    summarize(
        total_num = n(), 
        unsolved_num = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
        )

str(homicide_tidy)
```
* Create a `city_state` variable by combining the `city` and `state`
* Summarize within cities to obtain the total number of homicides(`total_num`) and the number of unsolved homicides(`unsolved_num`)
* Final dataset contains `r nrow(homicide_tidy)` observations and `r ncol(homicide_tidy)` variables. There are 3 variables including `city_state`, `total_num` and `unsolved_num`.

### 3. Solutions to the problems

#### a. For the city of Baltimore, MD, find the estimate and the CI of the unsolved homicides proportion.
```{r}
baltimore = 
    homicide_tidy %>% 
    filter(city_state == "Baltimore, MD")  

baltimore_prop = prop.test(baltimore$unsolved_num, baltimore$total_num)
    
baltimore_prop %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high) %>% 
    knitr::kable(digits = 3)
```

For the city of Baltimore, MD, the estimated proportion is 0.645 and the confidence interval is (0.628, 0.663)

#### b. Create a tidy dataframe with estimated proportions and CIs for each city
```{r, message=FALSE}
prop = function(x, n){
    prop.test(x, n) %>% 
        broom::tidy() %>% 
        select(estimate, conf.low, conf.high)
}

homicide_prop = 
    homicide_tidy %>% 
    mutate(prop = map2(.x = unsolved_num, .y = total_num, ~prop(x = .x, n = .y))) %>% 
    unnest() %>%  
    janitor::clean_names() %>% 
    select(-total_num, -unsolved_num) %>% 
    mutate(
        estimate = round(estimate, 3),
        conf_low = round(conf_low, 3),
        conf_high = round(conf_high, 3)
    ) 

str(homicide_prop)
```
We create a function to do `prop.test` and extract the estimate and the CI from the result. And then use `purrr::map2`, list columns and  unnest to create a tidy dataframe with estimated proportions and CIs for each city. Notably, for some cities Chi-squared approximation may be incorrect.

The homicide_prop dataset contains `r nrow(homicide_prop)` observations and `r ncol(homicide_prop)` variables including `city_state`, `estimate`, `conf_low` and `conf_high`.

#### c. Create a plot that shows the estimates and CIs for each city
```{r}
homicide_prop %>% 
    mutate(city_state = forcats::fct_reorder(city_state, estimate, .desc = T)) %>% 
    ggplot(aes(x = city_state, y = estimate)) +
    geom_errorbar(aes(x = city_state, ymin = conf_low, ymax = conf_high)) +
    geom_point(color = "blue") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(
        title = "Estimates and CIs of the Unsolved Homicides Proportion for Each City ",
        y = "Proportion Value",
        x = "City"
    )
```

From the plot we can know clearly that the estimated proportion of unsolved homicides in Chicago is the largest. 
